---
title       : Coursera Data Products Deck
subtitle    : Describes Loan Application Shiny Project
author      : Alan Walbeck
job         : Data Scientist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction - Good Loan Advisor

This is a pretty nifty little app that will take a fit model and allow anyone to then predict against the model using newdata that is uploaded via the web. It contains the following functionality

1. Provides "percent probability" values for the user
2. Provides a clear "YES" or "NO" answer for each loan application (in a table form) based on the value of the "percent probability" cut-off
3. Provides a tie back into the Loan ID

--- .class #id 

## Next Generation

The next generation solution is already in the works. It will provide:

1. The ability to "Upload" a completed file, including "percent probability" and "YES/NO" answers
2. The ability to perform single record queries (right now, it only does it in batch mode)
3. Email alert when completed

--- .class #id 

## Variable Importance

This report is provided once the dataset has been trained:
```{r}
load("PSCmodel2.RData")

varImpPlot(rf_fit, main="Variable Importance: PSC Dataset")
title(sub=paste(format(Sys.time(), "%Y-%b-%d %H:%M:%S")))
```

--- .class #id 

## Model Details

Below are the details for the model that was built.
```{r}
load("PSCmodel2.RData")
          
head(summary(rf_fit), 10)
```
